---
title: "MyFirstRMarkdown"
author: "Frank"
date: "02/14/2018"
output: 
  html_document: 
    number_sections: yes
    toc: yes
    toc_float: yes
--- 
```{r}
# toc means to include table of content
# toc_float means to include fancier table of content

# click knit to show the markdown in, for instance, html (what you've chosen)
```

# Single hashtag is a large header

Remember the hashtag? You don't need it to enter text normally!

## is a smaller header
why doesn't this work?

```{r}
# backtick is to the left of your 1 key
# i do need hashtags inside of code chunks to neter text!
# shortcut to insert a code chunk: command + option + i

2+2
```
### medium header
**BOLD** words by wrapping them in double stars.

_ITALICIZE_ words by wrapping them in underscores.

#### medium-small header
use the `backtick` to highlight text as code.

For example, i really like the `mean` function in R.

##### small header for puppies
click [here](https://montilab.psych.ucla.edu/wp-content/uploads/sites/49/2016/04/Motion-connectivity-analyses2.pdf) for puppies!

# this is section 2
```{r}
library(ggplot2) #load it in but no need to install.

```

